Sleep, relative to wake, increases both veridical and false memory in the DRM paradigm:

### 2023-07-11 manuscript.Rmd
Trying again

packagelist <- c('bookdown','knitr','rmarkdown','osfr','plyr','tidyr','dplyr','emmeans','ggplot2','Rmisc','buildmer','lme4','lmerTest','stringr','effects','effectsize','ggdist','car','gridExtra','kableExtra','rstatix','LSAfun','simr','effsize','readr')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

>>>>

packagelist <- c('bookdown','knitr','rmarkdown','osfr','plyr','tidyr','dplyr','emmeans','ggplot2','Rmisc','buildmer','lme4','lmerTest','stringr','effects','effectsize','ggdist','car','gridExtra','kableExtra')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

``` {r activate1}

library(rstatix)

``` {r activate2}

library(LSAfun)

``` {r activate3}

library(simr)

``` {r activate4}

library(effsize)

``` {r activate5}

library(readr)
